---
title: "Cocktails"
author: "Jackson M Luckey"
date: "5/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loadLibraries}
library(tidyverse)
```

```{r loadData}
cocktails <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-26/cocktails.csv')
```

Let's see what the most common ingredients are.

```{r mostCommonIngredients}
cocktails %>%
  group_by(ingredient) %>%
  count() %>%
  arrange(desc(n))
```

The two most common ingredients are vodka and gin. Since they are presumably the bases for different cocktails, lets see what ingredients commonly go with each one. To start off, we will create the dataframes `cocktails_vodka` and `cocktails_gin`, which each contain the cocktail recipes that contain the respective spirit.

```{r}
# returns a df containing drinks that use a particular ingredient
contains_ingredient <- function(ingredient_to_filter, df) {
  
  # create a vector that contains the id_drink of each cocktail that includes ingredient_to_filter
  tmp <- df %>%
    filter(ingredient == ingredient_to_filter)
  drink_ids <- tmp$id_drink
  
  # filter df to only contain cocktails where id_drink is in drink_ids
  df <- df %>%
    filter(id_drink %in% drink_ids)
  
  # return df
  df
  
}

cocktails_vodka <- contains_ingredient("Vodk", cocktails)
cocktails_gin <- contains_ingredient("Gin", cocktails)  
```

Now that we have `cocktails_vodka` and `cocktails_gin`, we can see if there is correlation between the base spirit in a cocktail and the other ingredients in said cocktail.

```{r tidyData}
# fix the measure column
# from manual checking with unique(cocktails$measure) the possible formats are:
# number + word(s) ("e.g. )
# number + measurement (e.g. "2 oz")
# number (e.g. "6)
# number can be an integer, decimal, fraction, or combination
```